Research on The Impact of Past Behaviour Normality on Regret

### 2024-02-15 outputs/paper/paper.qmd
scripts added

smith_regret_p <- round((mr_smith_counts / total_counts_1) * 100, 1)
smith_injunctive_p <- round((sum(data_filtered_1$sc1_socnorms1 == 2) / total_counts_1) * 100, 1)
smith_descriptive_p <- round((sum(data_filtered_1$sc1_socnorms2 == 2) / total_counts_1) * 100, 1)
smith_negative_p <- round((sum(data_filtered_1$sc1_combinednorms == 2) / total_counts_1) * 100, 1)
jones_regret_p <- round((mr_jones_counts / total_counts_1) * 100, 1)
jones_injunctive_p <- round((sum(data_filtered_1$sc1_socnorms1 == 1) / total_counts_1) * 100, 1)
jones_descriptive_p <- round((sum(data_filtered_1$sc1_socnorms2 == 1) / total_counts_1) * 100, 1)
jones_negative_p <- round((sum(data_filtered_1$sc1_combinednorms == 1) / total_counts_1) * 100, 1)

>>>>

# calculate each percentage
smith_regret_p <- round((mr_smith_counts / total_counts_1) * 100, 1)
smith_injunctive_p <- round((sum(data_filtered_1$sc1_socnorms1 == 2) / total_counts_1) * 100, 1)
smith_descriptive_p <- round((sum(data_filtered_1$sc1_socnorms2 == 2) / total_counts_1) * 100, 1)
smith_negative_p <- round((sum(data_filtered_1$sc1_combinednorms == 2) / total_counts_1) * 100, 1)
jones_regret_p <- round((mr_jones_counts / total_counts_1) * 100, 1)
jones_injunctive_p <- round((sum(data_filtered_1$sc1_socnorms1 == 1) / total_counts_1) * 100, 1)
jones_descriptive_p <- round((sum(data_filtered_1$sc1_socnorms2 == 1) / total_counts_1) * 100, 1)
jones_negative_p <- round((sum(data_filtered_1$sc1_combinednorms == 1) / total_counts_1) * 100, 1)
